fastText Supervised Classifier

### 2019-05-08 Code/dallin_annotations/04_build_fasttext_supervised_classifier.Rmd
Created a visualization of the accuracy of the fastText model, along with a few notes explaining our thought process behind making the model.

@@

!!!!!!!!!! I'm still not sure how we are using the test_labels_without_prefix. If its not the test data, what is it?

@@

This will help us confirm that our model worked as expected. The predictions are shorter than the test dataset, so I'm not sure what happened. According to some errors I've seen, I think it's because a few tweets use vocabulary that was not included in the training dataset.
```{r}
length(predictions)
length(test_labels_without_prefix)
length(test_data_lines)
```

A second attempt to make predictions:
```{r error = TRUE}
tested <- test_train_data %>% 
  filter(test_train == "test") %>% 
  mutate(prediction = predict(model, tweet_text, unlock_empty_predictions = TRUE)) %>% 
  unnest(prediction) %>% 
  mutate(rounded_prediction = round(prediction),
         correct            = case_when(complaint_label == rounded_prediction ~ TRUE,
                                        complaint_label != rounded_prediction ~ FALSE))
```

Visualization of Outputs:
From this graph, apparently I messed up somewhere in making predictions, because the predictions being made seem to have no correlation with the actual complaint label. It could be that, or the fastText model needs significantly more text to train and be accurate. 
```{r}
tested %>% 
  ggplot(aes(x = row_number(tweet_text), y = prediction, color = complaint_label, alpha = 0.1)) +
  geom_point()
```

Is the list "predictions" the same as the "prediction" variable in tested?
```{r}
are_they_same <- c(tested$prediction[[3]],
                   predictions[[3]],
                   tested$prediction[[300]],
                   predictions[[300]])

(are_they_same)
```
The predictions are exactly the same from both sets, so I guess the classifier was just bad?

I'll try to use our fasttext model using bash.
Navigate to the right directory of the model:
```{bash error = TRUE}
cd ../../Output/models/class_mod_1.bin
ls
```

```{bash error = TRUE}
./fasttext predict ../../Output/models/class_mod_1.bin - @delta you are the worst airline. Thanks for delaying my flight
```
This didn't work

Second attempt to make predictions using bash
```{bash error = TRUE}
cd ../../Output/models

./fasttext predict class_mod_1.bin - @delta you are the worst airline. Thanks for delaying my flight
```

Third attempt to make predictions using bash.
```{bash error = TRUE}
cd ../../../../../../fasttext/fastText-0.2.0
ls
```

f## Accuracy
Let's look at how accurately the model predicted names
```{r error = TRUE}
# Compute accuracy
mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
```

@@

# Analysis

>>>>

The supervised model built in this script is not used in the "frankenstien model." Instead, it is a standalone classification model. This is a way for us to compare the frankenstien model's performance to a "baseline."

@@

@@

Below we compare the length of the list of predictions to the length of the testing dataset. Ideally, these should have the same length. This will help us confirm that our model worked as expected.

```{r}
length(predictions)
length(test_labels_without_prefix)
length(test_data_lines)
```

Unexpectedly, the predictions are shorter than the test dataset, so I'm not sure what happened. According to some errors I've seen, I think it's because a few tweets use vocabulary that was not included in the training dataset.

Below, we merge the predictions with our testing dataset, preparing the data for visualizations.
```{r}
new_predictions <- attributes(predictions)$names

tested <- test_train_data %>% 
  filter(test_train == "test") %>% 
  mutate(prediction = predict(model, tweet_text, unlock_empty_predictions = TRUE)) %>% 
  unnest(prediction) %>% 
  mutate(new_predictions = new_predictions,
         correct = case_when(label == new_predictions ~ TRUE,
                             label != new_predictions ~ FALSE))
```

Visualization of Outputs:
Below, we have a bar graph of our testing data and the model's predictions. The columns represent the labels from our testing dataset. The fill is the model's predictions. We see that the model seems to make a lot of false positives, but provides almost no false negatives. 
```{r}
tested %>% 
  ggplot(aes(x = label, fill = new_predictions)) +
  geom_bar()
```

## Accuracy
Let's look at how accurately the model predicted binary complaints.
```{r}
tested %>% 
  summarise(accuracy = mean(correct))
```
It looks like this model is about 60% accurate. This isn't great, but it's better than flipping a coin. Perhaps the model will perform significantly better with a larger dataset for training and testing.

```{r error = TRUE}
# Compute accuracy
mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
```

@@
